\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-08 doc/paper.tex
removed detailed explanation of VEV problem. I think there is no way to include this, but perhaps Jae-hyeon or Alex can suggest a cleanerf fix that is more suitable.

Nonetheless \fs provides help for such cases in several ways. One may
adjust initial guesses specified in the FlexibleSUSY model file, such
as changing the choice of \code{HighScaleFirstGuess} or altering
\code{HighScaleMinimum} and \code{HighScaleMaximum} which can be used
to push the iteration back towards where the solution should be if it
gets off track.

For experienced users the clear code structure also allows the
possibility of direct adaption of the code.  For example in the case
of the E6SSM we observed that for some points the presence of new
Yukawas had a big impact on the RGEs for the VEVs.  When the user
chooses to set these Yukawas at the GUT scale, then on the initial run
up to the GUT scale they will be set to zero.  As a result the VEV
RGEs on the run up are quite different to the VEV RGEs on the run down
so that the VEVs used at the SUSY scale are far from the correct
values and this can create an instability leading eventually to
non-perturbative in the couplings.  This can be fixed by adapting the
algorithm so that the VEVs are stored at the SUSY scale.  However a
simpler, if less clean, fix is to directly modify the generated code
by adding three lines to the file
\code{<model>_two_scale_susy_parameters.cpp} just before the beta
functions are returned in method
\code{<model>_susy_parameters::calc_beta()}.

\code{ 
if(get_scale()  > 3.0e3) beta_vd =0;
if(get_scale()  > 3.0e3) beta_vu =0;
if(get_scale()  > 3.0e3) beta_vs =0;
return E6SSMnew_susy_parameters(get_scale(), get_loops(), get_thresholds(), input,
beta_Yd, beta_Ye, beta_Kappa, beta_Lambda12, beta_Lambdax, beta_Yu, beta_MuPr, beta_g1, beta_g2, beta_g3, beta_g1p, beta_vd, beta_vu, beta_vs);
}

>>>>

Nonetheless \fs provides help for such cases in several ways. One may
adjust initial guesses specified in the FlexibleSUSY model file, such
as changing the choice of \code{HighScaleFirstGuess} or altering
\code{HighScaleMinimum} and \code{HighScaleMaximum} which can be used
to push the iteration back towards where the solution should be if it
gets off track.For experienced users the clear code structure also allows the
possibility of direct adaption of the code.
